---
title: "NAME OF THE TUTORIAL"
author: "Peter Baumgartner"
description: "SHORT DESCRIPTION OF THE TUTORIAL"
output:
  learnr::tutorial:
    progressive: false
    allow_skip: true
    theme: "cerulean"
    css: "css/style.css"
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Topic 1

### Exercise 

<object data=https://peter.baumgartner.name/wp-admin/admin-ajax.php?action=h5p_embed&id=349 width="960" height="475"> <embed src=https://peter.baumgartner.name/wp-admin/admin-ajax.php?action=h5p_embed&id=349 width="960" height="475"> </embed> Error: Embedded data could not be displayed. </object>

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

<iframe src="https://peter.baumgartner.name/wp-admin/admin-ajax.php?action=h5p_embed&id=349" width="960" height="475" frameborder="0" allowfullscreen="allowfullscreen" title="ims-01: Variable Types (T/F Battery)"></iframe><script src="https://peter.baumgartner.name/wp-content/plugins/h5p/h5p-php-library/js/h5p-resizer.js" charset="UTF-8"></script>



### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

```{r}
knitr::include_app("https://gallery.shinyapps.io/001-hello/", height = "500px")
```


### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

<iframe width="560" height="315" src="https://www.youtube.com/embed/wvfI7yGZAHc" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

## Topic 3

```{r}
knitr::include_url("https://peter.baumgartner.name/wp-admin/admin-ajax.php?action=h5p_embed&id=349")
```

